Données de vaccination et 

### 2021-10-06 code/manhattan_animated.Rmd

  LOG_OR_1107 = questionr::odds.ratio(LOG_1107$`1ry_res`, LOG_1107$taux_cumu_1_inj) %>%
    rbind(questionr::odds.ratio(LOG_1107$`2ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Vacant_Home`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Houses`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Flats`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Nb_Rooms_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`House_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Flat_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_bf_1919`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_19-45`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_46-70`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_71-90`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_91-05`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_06-15`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_lt2y`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_2to4y`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_5to9y`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_10to19y`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_20to29y`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_gt30y`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Owner`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Tenant`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Social`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_FreeAcc`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Carpark`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_0car`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_1car`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_2car`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_3+car`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_gt0car`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Owner`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Tenant`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Social`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_FreeAcc`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Owners_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Tenant_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Social_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`FreeAcc_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Overcrowding_rate`, LOG_1107$taux_cumu_1_inj)) %>%
    as.data.frame() %>%
    bind_cols(Variable = colnames(LOG_1107)[2:42]) %>%
    select(Variable, OR, `2.5 %`, `97.5 %`, p)
  rownames(LOG_OR_1107) = NULL
  # write_csv2(LOG_OR, "data/LOG_OR.csv")

@@

    rbind(questionr::odds.ratio(EMP_1107$`1524_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%

@@

    rbind(questionr::odds.ratio(EMP_1107$`5564_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%

@@

    rbind(questionr::odds.ratio(EMP_1107$`1564_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1524_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`2554_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`5564_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%

@@

    rbind(questionr::odds.ratio(EMP_1107$`2554_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%

@@

    rbind(questionr::odds.ratio(EMP_1107$`1564_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%

@@

    rbind(questionr::odds.ratio(EMP_1107$`2554_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%

@@

    rbind(questionr::odds.ratio(EMP_1107$`2554_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%

@@

    rbind(questionr::odds.ratio(EMP_1107$`1564_NonWorking_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%

@@

    rbind(questionr::odds.ratio(EMP_1107$`1564_men_Unemplyed_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_women_Unemplyed_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%

@@

    rbind(questionr::odds.ratio(EMP_1107$`15+_Salaried_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%

@@

    rbind(questionr::odds.ratio(EMP_1107$`15+_FullTime_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%

@@

    rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%

@@

    rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_nonsalWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_FullTimeWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_FullTimeWF`, EMP_1107$taux_cumu_1_inj)) %>%

@@

    bind_cols(Variable = colnames(EMP_1107)[2:63]) %>%

@@

    rbind(questionr::odds.ratio(FAM_1107$`Family_HH`, FAM_1107$taux_cumu_1_inj)) %>%

@@

    rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleMan_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleWoman_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_OtherNoFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_Family_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_NoChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_ChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleParent_HH`, FAM_1107$taux_cumu_1_inj)) %>%

@@

    rbind(questionr::odds.ratio(FAM_1107$`Pop_CraftsBusinessShopkeepers_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_HighQualidied_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_Intermediate_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_BlueCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%

@@

    rbind(questionr::odds.ratio(FAM_1107$`Pop_Retired_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_Other_HH`, FAM_1107$taux_cumu_1_inj)) %>%

@@

    rbind(questionr::odds.ratio(FAM_1107$`15+_nonMarried_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`1524_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`2554_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`5579_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`80+_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%

@@

    rbind(questionr::odds.ratio(FAM_1107$`Family_w_Children_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Single_Parent_Family_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Family_wo_Children_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%

@@

    bind_cols(Variable = colnames(FAM_1107)[2:51]) %>%

@@

  REV_OR_1107 = questionr::odds.ratio(REV_1107$`D1_st_Living`, REV_1107$taux_cumu_1_inj) %>%
    rbind(questionr::odds.ratio(REV_1107$`Median_st_Living`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`D9_st_Living`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Interdecile_91_Ratio`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Taxable_HH`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Poverty_amg_Owners`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Poverty_amg_Tenants`, REV_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(REV_1107$`-30_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(REV_1107$`3039_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(REV_1107$`4049_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(REV_1107$`5059_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(REV_1107$`6074_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(REV_1107$`75+_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Poverty`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Activity_Income`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Salary_Income`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Unemployment_Benef`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Self-Employment`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Pensions_Annuities`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Estate`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Social_Benef`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Family_Benef`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Social_Minima`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Housing_Benef`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Tax`, REV_1107$taux_cumu_1_inj)) %>%
    as.data.frame() %>%
    bind_cols(Variable = colnames(REV_1107)[c(2:8, 15:26)]) %>%
    select(Variable, OR, `2.5 %`, `97.5 %`, p)
  rownames(REV_OR_1107) = NULL
  # write_csv2(REV_OR, "data/REV_OR.csv")

  ACT_OR_1107 = questionr::odds.ratio(ACT_1107$`Wk_Res_Municipality`, ACT_1107$taux_cumu_1_inj) %>%
    rbind(questionr::odds.ratio(ACT_1107$`Wk_Res_County-Municipality`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`Wk_Res_Region-County`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`Wk_Res_Country-Region`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`Wk_Dom_Com_Abroad`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`noTransport_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`Walk_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`Bike_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`Motorbike_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`Drive_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`PublicTrans_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`15+_Men_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`15+_Women_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(ACT_1107$`15+_PermanentContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(ACT_1107$`15+_ShortTermContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(ACT_1107$`15+_InterimContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(ACT_1107$`15+_SubsidizedWork_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(ACT_1107$`15+_ApprenticeContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(ACT_1107$`15+_SelfEmployed_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(ACT_1107$`15+_Employers_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(ACT_1107$`15+_caregivers_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
    as.data.frame() %>%
    bind_cols(Variable = colnames(ACT_1107)[2:14]) %>%
    select(Variable, OR, `2.5 %`, `97.5 %`, p)
  rownames(ACT_OR_1107) = NULL
  # write_csv2(ACT_OR, "data/ACT_OR.csv")

>>>>

  LOG_OR_1107 = questionr::odds.ratio(LOG_1107$`1ry_res`, LOG_1107$taux_cumu_1_inj) %>%
    # rbind(questionr::odds.ratio(LOG_1107$`2ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Vacant_Home`, LOG_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(LOG_1107$`Houses`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Flats`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Nb_Rooms_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(LOG_1107$`House_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(LOG_1107$`Flat_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_bf_1919`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_19-45`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_46-70`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_71-90`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_91-05`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_06-15`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_lt2y`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_2to4y`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_5to9y`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_10to19y`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_20to29y`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_gt30y`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Owner`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Tenant`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Social`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_FreeAcc`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Carpark`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_0car`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_1car`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_2car`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_3+car`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(LOG_1107$`1ry_res_gt0car`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Owner`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Tenant`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Social`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_FreeAcc`, LOG_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(LOG_1107$`Owners_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(LOG_1107$`Tenant_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Social_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(LOG_1107$`FreeAcc_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(LOG_1107$`Overcrowding_rate`, LOG_1107$taux_cumu_1_inj)) %>%
    as.data.frame() %>%
    bind_cols(Variable = colnames(LOG_1107)[c(2, 4, 6:7, 10:31, 33:36, 40)]) %>%
    select(Variable, OR, `2.5 %`, `97.5 %`, p)
  rownames(LOG_OR_1107) = NULL
  # write_csv2(LOG_OR, "data/LOG_OR.csv")

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

    bind_cols(Variable = colnames(EMP_1107)[c(2:6, 8, 10:13, 19, 21, 23, 25:27, 29, 31:33, 36:53, 55, 57, 59, 63)]) %>%

@@

@@

@@

@@

@@

@@

@@

    bind_cols(Variable = colnames(FAM_1107)[c(2:5, 7:18, 26, 31, 34:39, 45:48)]) %>%

@@

  REV_OR_1107 = questionr::odds.ratio(REV_1107$`D1_st_Living`, REV_1107$taux_cumu_1_inj) %>%
    rbind(questionr::odds.ratio(REV_1107$`Median_st_Living`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`D9_st_Living`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Interdecile_91_Ratio`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Taxable_HH`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Poverty_amg_Owners`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Poverty_amg_Tenants`, REV_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(REV_1107$`-30_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(REV_1107$`3039_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(REV_1107$`4049_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(REV_1107$`5059_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(REV_1107$`6074_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(REV_1107$`75+_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Poverty`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Activity_Income`, REV_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(REV_1107$`Salary_Income`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Unemployment_Benef`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Self-Employment`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Pensions_Annuities`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Estate`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Social_Benef`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Family_Benef`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Social_Minima`, REV_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(REV_1107$`Housing_Benef`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Tax`, REV_1107$taux_cumu_1_inj)) %>%
    as.data.frame() %>%
    bind_cols(Variable = colnames(REV_1107)[c(2:8, 15:16, 18:24, 26)]) %>%
    select(Variable, OR, `2.5 %`, `97.5 %`, p)
  rownames(REV_OR_1107) = NULL
  # write_csv2(REV_OR, "data/REV_OR.csv")

  ACT_OR_1107 = questionr::odds.ratio(ACT_1107$`Wk_Res_Municipality`, ACT_1107$taux_cumu_1_inj) %>%
    rbind(questionr::odds.ratio(ACT_1107$`Wk_Res_County-Municipality`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`Wk_Res_Region-County`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`Wk_Res_Country-Region`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`Wk_Dom_Com_Abroad`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`noTransport_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`Walk_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`Bike_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`Motorbike_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`Drive_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`PublicTrans_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`15+_Men_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(ACT_1107$`15+_Women_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(ACT_1107$`15+_PermanentContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(ACT_1107$`15+_ShortTermContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(ACT_1107$`15+_InterimContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(ACT_1107$`15+_SubsidizedWork_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(ACT_1107$`15+_ApprenticeContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(ACT_1107$`15+_SelfEmployed_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(ACT_1107$`15+_Employers_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
    # rbind(questionr::odds.ratio(ACT_1107$`15+_caregivers_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
    as.data.frame() %>%
    bind_cols(Variable = colnames(ACT_1107)[2:13]) %>%
    select(Variable, OR, `2.5 %`, `97.5 %`, p)
  rownames(ACT_OR_1107) = NULL
  # write_csv2(ACT_OR, "data/ACT_OR.csv")
